Les besoins en éducation pour les pratiques opensource

### 2022-02-03 main.tex
bib: make the bibliography work with APA7 style
Allow to build indexes and glossaries

% Load packages for testing
\usepackage{blindtext}
%\usepackage{showframe} % Uncomment to show boxes around the text area, margin, header and footer
%\usepackage{showlabels} % Uncomment to output the content of \label commands to the document where they are used

% Load the bibliography package
\usepackage{kaobiblio}
\addbibresource{references.bib} % Bibliography file

@@

\makeindex[columns=3, title=Alphabetical Index, intoc] % Make LaTeX produce the files required to compile the index

@@

\Blindtext

@@

\Blinddocument

@@

\Blinddocument

@@

\pagelayout{wide} % No margins
\addpart{Appendices}
\pagelayout{margin} % Restore margins

\chapter{Some more blindtext}

\Blinddocument

@@

\printindex % Output the index

>>>>

% Load the bibliography package
\usepackage[style=apa]{kaobiblio}
\addbibresource{references.bib} % Bibliography file

@@

\makeindex[columns=3, title=Alphabetical Index, intoc] % Make LaTeX produce the files required to compile the index
\makeglossaries % make latex produce the files required to compile the glossary

\newacronym{gpl}{GPL}{GNU General Public License}
\newacronym{cc}{CC}{Creative Commons}

@@

@@

Une référence pertinente (\sidecite{strategies-2012}).

Un exemple d'index\index{index}.

Je ne suis pas sûr que je vais souvent\index{souvent} utiliser des
index\index{index} cependant.

Un élément de glossaire serait le \acrshort{gpl}.

Et les glossaires par contre je risque de plus souvent les utiliser, par exemple
pour parler de licences comme la \acrlong{gpl} ou la \acrshort{cc}.

@@

@@

\pagelayout{wide} % No margins
\addpart{Annexes}
\pagelayout{margin} % Restore margins

\chapter{Première annexe}

@@

\printindex % Output the index
\printglossary % Output the glossary
